\documentclass[a4paper,10pt]{amsart}

\input{pream/prambolo}
\author{Fosco Loregian}
\title{A construction with Yoneda structures}
\begin{document}
\maketitle
\begin{abstract}
In $\Cat$, we call an object \emph{$\mu$-presentable} (for $\mu$ a regular cardinal) when $\hom(a,\firstblank)$ commutes with $\mu$-filtered colimits. 
\begin{itemize}
\item A category $\iC$ is $\mu$-\emph{accessible} when it has a small subcategory $\iG\subseteq \iC$ whose objects are all $\mu$-presentable and such that every object of $\iC$ is a $\mu$-filtered colimit of objects in $\iG$ (such a $\iG$ is called a \emph{generator} for $\iC$). 
\item A category $\iC$ is called \emph{locally $\mu$-presentable} if it is $\mu$-accessible and cocomplete (equivalently, $\mu$-accessible and complete).
\end{itemize}
I want to reproduce these two definitions inside a 2-category $\clK$ with a Yoneda structure. To do it, I take the definitions in $\Cat$ and try to rephrase them formally so that they become straighforwardly referred to the 0-,1- and 2-cells in $\clK$.
\end{abstract}
\begin{claim*}
There is a monad $T_{\iC,\mu}$ on $[\iC,\Set]$ such that $T_{\iC}(F)\cong F$ iff $F$ commutes with $\mu$-filtered colimits.
\end{claim*}
The unit of this monad induces by restriction a 2-cell
\[
\xymatrix{
	\iC^\opp \ar[r]^y \ar[d]_y \ar@{}[dr]|(.3){\alpha\Swarrow} & [\iC,\Set]\\
	[\iC,\Set]\ar[ur]_{T_{\iC,\mu}} & 
}
\]
Now if $\iC$ has a generator $\iG$, composing with $j : \iG \to \iC$ one has $\alpha * j : Tyj(a)\cong yj(a) = \hom(a,\firstblank)$, since all objects $\iG$ are $\mu$-presentable.

The fact that every object in $\iC$ is a colimit of objects in $\iG$ can be expressed by saying that $j$ is dense: $\Lan_jj\cong 1$.  So, it seems that
\begin{claim*}
$\iC$ is $\mu$-accessible iff
\begin{itemize}
	\item it has a dense generator $j : \iG\to \iC$,
	\item such that if $\alpha := \eta * y$ is the restriction of the unit of $T_{\iC,\mu}$ to representables, the whiskering $\alpha * j$ is invertible.
\end{itemize}
\end{claim*}
Is it possible to find $T$? If yes, we're really near to define accessible and locally presentabile objects in $\clK$ with a YS: in fact, the definition of locally presentable is way easier: since $\iC$ is locally presentable if it is a localization of a category of presheaves, it seems enough to say that $\iC$ is locally presentable if it has a generator $j$ such that $\iG(j,1)$ has a left adjoint and it is fully faithful.

I would like to know
\begin{itemize}
\item if this circle of ideas makes any sense at all; has anybody tried to do ``the formal category theory of locally presentable and accessible objects''?
\item if (and how) the existence of $T$ can be verified, and when it exists in $\clK \neq\Cat$ what is its definition; I expect it to exist as a consequence of a specific property of $\clK$ (or maybe even from a new axiom?)
\item if the necessity to work with the \emph{contravariant} Yoneda in
\[
\xymatrix{
	\iC^\opp \ar[r]^y \ar[d]_y \ar@{}[dr]|(.3){\alpha\Swarrow} & [\iC,\Set]\\
	[\iC,\Set]\ar[ur]_{T_{\iC,\mu}} & 
}
\]
poses a problem: are we dealing with a\dots right Yoneda structure (ie with right extensions and liftings)? If yes, can the theorems about these dualized Yoneda structure be dualized in the straightforward way?
\end{itemize}

\bibliography{allofthem}{}
\bibliographystyle{amsalpha}
\hrulefill 
\end{document}